### 2013-07-24 doc/asplos14/evaluation.tex
add latency exploration

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{results/plot_concurrency.pdf}
    \end{center}
    \caption{Throughput, request latency, and idleness as number of concurrent workers is varied}
    \label{fig:grappa-concurrency}
\end{figure}

\paragraph{How much concurrency does \Grappa require? How much latency does it add?}
Figure~\ref{fig:grappa-concurrency} shows 
UTS blocks at ea
\todo{FINISH}

@@

\todo{FINISH}
Our current

>>>>

\begin{figure}[ht]
    \begin{center}
      \includegraphics[height=0.5\textwidth]{results/plot_concurrency.pdf}
    \end{center}
    \caption{Throughput, request latency, and idleness as number of concurrent workers is varied}
    \label{fig:grappa-concurrency}
\end{figure}

\paragraph{How much concurrency does \Grappa require? How much latency does it add?}
\Grappa depends on concurrency to cover the latency of aggregation and
remote communication. How much is required for good performance?

Figure~\ref{fig:grappa-concurrency} shows a 48-node, 16-core-per-node
run of UTS, varying the number of concurrently executing tasks on each
core. The top pane shows the overall throughput of the tree search.
The middle pane shows average blocking delegate operation latency in
microseconds. The bottom pane shows idle time; that is, the fraction
of the time the scheduler could not find a ready task to run.

We can observe three things from this figure. First, above 512
concurrently executing tasks per core, idle time is practically zero:
these tasks generate requests fast enough to cover the latency of
aggregation and communication. This matches the results seen in the
throughput plot; throughput peaks at 512 workers and gradually
decreases after that due to the overhead of unnecessary context
switches. Finally, we see that with 512 workers, the average
per-request latency is $~$1.8ms.

@@

\TODO{FINISH}
Our current
